Guilt, shame, and anti-war action in an authoritarian country at war

### 2023-04-30 manuscript.tex
Switched to p_format for formatting p-values

\caption{\label{tab:Table1}Predicting group-based guilt and shame from political beliefs}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llccccccccccc}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Moral Shame} & \multicolumn{4}{c}{Image Shame} & \multicolumn{4}{c}{Guilt} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
  & $\beta$ & $b$ & $SE$ & $p$ & $\beta$ & $b$ & $SE$ & $p$ & $\beta$ & $b$ & $SE$ & $p$\\
\midrule
Intercept & 0 & -2.89 & 0.32 & <0.001 & 0 & -2.850 & 0.34 & <0.001 & 0 & -2.930 & 0.34 & <0.001\\
Democratic Values & 0.41 & 0.64 & 0.05 & <0.001 & 0.4 & 0.640 & 0.05 & <0.001 & 0.41 & 0.650 & 0.05 & <0.001\\
Political Cynicism (politicians) & 0.18 & 0.20 & 0.05 & <0.001 & 0.16 & 0.180 & 0.05 & <0.001 & 0.09 & 0.100 & 0.05 & 0.039\\
Political Cynicism (politics) & -0.05 & -0.05 & 0.04 & 0.189 & -0.03 & -0.030 & 0.04 & 0.458 & -0.03 & -0.030 & 0.04 & 0.455\\
Political Alienation & -0.05 & -0.06 & 0.04 & 0.122 & -0.03 & -0.040 & 0.04 & 0.380 & 0.01 & 0.020 & 0.04 & 0.663\\
\addlinespace
Political Responsibility & 0.04 & 0.05 & 0.04 & 0.190 & 0.03 & 0.040 & 0.04 & 0.347 & 0.07 & 0.100 & 0.04 & 0.022\\
\midrule
R$^{2}$ &  & 0.26 &  &  &  & 0.234 &  &  &  & 0.221 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:Table2}Predicting anti-war action from group-based guilt and shame}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lllllllllllll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Past Behaviour} & \multicolumn{4}{c}{Behavioural Intention} & \multicolumn{4}{c}{Action Probability} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
  & $\beta$ & b & SE & p & $\beta$ & b & SE & p & $\beta$ & b & SE & p\\
\midrule
Intercept & 0 & 0.1 & 0.04 & 0.0094 & 0 & 1.09 & 0.03 & <0.001 & 0 & 1.21 & 0.07 & <0.001\\
Guilt & 0.02 & 0.01 & 0.04 & 0.7562 & 0 & 0 & 0.03 & 0.942 & 0.05 & 0.06 & 0.06 & 0.326\\
Image Shame & -0.07 & -0.05 & 0.05 & 0.3926 & 0.1 & 0.06 & 0.04 & 0.154 & -0.02 & -0.02 & 0.1 & 0.826\\
Moral Shame & 0.48 & 0.31 & 0.06 & <0.001 & 0.56 & 0.33 & 0.05 & <0.001 & 0.59 & 0.77 & 0.11 & <0.001\\
\midrule
R$^{2}$ &  & 0.181 &  &  &  & 0.425 &  &  &  & 0.376 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

Behavioral intentions and action probability correlated at \emph{r} = 0.86, \emph{p} \textless0.001, so we scaled and combined the two measures into a single indicator of future anti-war action. We ran a linear regression predicting future anti-war behavior from attitude towards the war, negative and positive emotions, and shame and guilt. Table \ref{tab:Table3} presents the results. Overall, the model explained 47\% of variance in future behavior. Anti-war behavioral intentions were best predicted by moral shame (\(\beta\) = 0.36, \emph{p} \textless0.001), followed by negative dominant emotions (\(\beta\) = 0.24, \emph{p} \textless0.001), and only then attitude (\(\beta\) = -0.15, \emph{p} \textless0.001). Negative submissive emotions had a small negative effect on intentions to act (\(\beta\) = -0.08, \emph{p} = 0.015).

@@

\caption{\label{tab:Table3}Predicting future behavior from emotions and attitudes
}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllll}
\toprule
  & $\beta$ & b & SE & t-value & p\\
\midrule
Intercept & 0 & -0.1 & 0.12 & -0.82 & 0.410\\
Emotions: Positive & -0.032 & -0.03 & 0.03 & -0.96 & 0.337\\
Emotions: Negative Dominant & 0.237 & 0.19 & 0.03 & 6.4 & <0.001\\
Emotions: Negative Submissive & -0.076 & -0.07 & 0.03 & -2.43 & 0.015\\
Attitudes towards the war & -0.152 & -0.12 & 0.03 & -3.77 & <0.001\\
\addlinespace
Group-based moral shame & 0.36 & 0.22 & 0.05 & 4.63 & <0.001\\
Group-based image shame & 0.002 & 0 & 0.04 & 0.03 & 0.977\\
Group-based guilt & 0.033 & 0.02 & 0.03 & 0.76 & 0.450\\
\bottomrule
\end{tabular}
\end{table}

The results of the zero-inflated negative binomial model (Table \ref{tab:TableS4}, SM) suggested that different predictors account for the presence vs.~absence of intentions to act versus the strength of these intentions. Only moral shame (\emph{b} = -.36, \emph{p} = .036) and attitude (\emph{b} = .38, \emph{p} = .001) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (\emph{b} = .24, \emph{p} \textless{} .001), whereas negative submissive emotions predicted weaker intentions to act (\emph{b} = -.14, \emph{p} = .013).

@@

\caption{\label{tab:TableS1}Path model predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllll}
\toprule
  & $\beta$ & b & SE & t-value & p\\
\midrule
Intercept & 0 & -0.1 & 0.12 & -0.82 & 0.410\\
Emotions: Positive & -0.032 & -0.03 & 0.03 & -0.96 & 0.337\\
Emotions: Negative Dominant & 0.237 & 0.19 & 0.03 & 6.4 & <0.001\\
Emotions: Negative Submissive & -0.076 & -0.07 & 0.03 & -2.43 & 0.015\\
Attitudes towards the war & -0.152 & -0.12 & 0.03 & -3.77 & <0.001\\
\addlinespace
Group-based moral shame & 0.36 & 0.22 & 0.05 & 4.63 & <0.001\\
Group-based image shame & 0.002 & 0 & 0.04 & 0.03 & 0.977\\
Group-based guilt & 0.033 & 0.02 & 0.03 & 0.76 & 0.450\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS2}Zero-inflated negative binomial regression predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrr}
\toprule
\multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Moral Shame}} & \multicolumn{3}{c}{\textbf{Image Shame}} & \multicolumn{3}{c}{\textbf{Guilt}} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
\em{ } & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & -0.76 & 0.31 & 0.014 & -0.44 & 0.29 & 0.129 & -0.85 & 0.28 & 0.002\\
Democratic values & 0.23 & 0.05 & <0.001 & 0.17 & 0.05 & <0.001 & 0.25 & 0.05 & <0.001\\
Political cynicism (politicians) & 0.12 & 0.05 & 0.006 & 0.12 & 0.04 & 0.005 & 0.07 & 0.04 & 0.065\\
Political cynicism (politics) & -0.04 & 0.03 & 0.172 & -0.03 & 0.03 & 0.253 & -0.02 & 0.03 & 0.548\\
\addlinespace
Political alienation & -0.03 & 0.03 & 0.255 & <0.001 & 0.03 & 0.971 & <0.001 & 0.03 & 0.992\\
Political responsibility & 0.01 & 0.03 & 0.691 & <0.001 & 0.03 & 0.948 & 0.03 & 0.03 & 0.308\\
\midrule
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 5.03 & 0.63 & <0.001 & 5.15 & 0.62 & <0.001 & 4.17 & 0.6 & <0.001\\
Democratic values & -0.74 & 0.1 & <0.001 & -0.77 & 0.1 & <0.001 & -0.67 & 0.09 & <0.001\\
\addlinespace
Political cynicism (politicians) & -0.05 & 0.09 & 0.529 & -0.06 & 0.08 & 0.493 & 0.05 & 0.08 & 0.569\\
Political cynicism (politics) & -0.11 & 0.07 & 0.115 & -0.11 & 0.07 & 0.123 & -0.07 & 0.07 & 0.315\\
Political alienation & 0.02 & 0.07 & 0.73 & 0.04 & 0.07 & 0.579 & -0.06 & 0.07 & 0.369\\
Political responsibility & -0.05 & 0.07 & 0.528 & -0.05 & 0.07 & 0.492 & -0.07 & 0.07 & 0.295\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS3}Predicting anti-war action from group-based shame and guilt}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrr}
\toprule
\multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Past behavior}} & \multicolumn{3}{c}{\textbf{Behavioral inention}} & \multicolumn{3}{c}{\textbf{Action probability}} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
\em{ } & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 0.65 & 0.16 & <0.001 & -0.22 & 0.15 & 0.142 & 0.39 & 0.1 & <0.001\\
Guilt & 0 & 0.07 & 0.953 & -0.03 & 0.05 & 0.53 & 0.02 & 0.04 & 0.606\\
Image shame & -0.09 & 0.09 & 0.313 & 0 & 0.08 & 0.988 & 0.02 & 0.06 & 0.671\\
Moral shame & 0.08 & 0.1 & 0.451 & 0.25 & 0.08 & 0.003 & 0.22 & 0.07 & 0.001\\
\midrule
\addlinespace
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 2.72 & 0.19 & <0.001 & 1.7 & 0.2 & <0.001 & 1.4 & 0.14 & <0.001\\
Guilt & -0.05 & 0.13 & 0.696 & -0.18 & 0.13 & 0.156 & -0.2 & 0.09 & 0.033\\
Image shame & -0.18 & 0.17 & 0.295 & -0.47 & 0.26 & 0.076 & -0.13 & 0.14 & 0.384\\
Moral shame & -0.65 & 0.19 & 0.001 & -0.26 & 0.27 & 0.337 & -0.35 & 0.16 & 0.033\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS4}Predicting future behavior from emotions and attitudes.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrr}
\toprule
\em{ } & \em{b} & \em{SE} & \em{z-value} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 1.63 & 0.23 & 7.05 & <0.001\\
Emotions: Positive & -0.08 & 0.08 & -1.06 & 0.287\\
Emotions: Negative dominant & 0.24 & 0.06 & 4.32 & <0.001\\
Emotions: Negative submissive & -0.14 & 0.05 & -2.49 & 0.013\\
\addlinespace
Attitude to the war & -0.12 & 0.07 & -1.84 & 0.066\\
Group-based moral shame & 0 & 0.06 & -0.05 & 0.964\\
Group-based image shame & 0.08 & 0.05 & 1.5 & 0.133\\
Group-based guilt & 0.05 & 0.04 & 1.51 & 0.132\\
\midrule
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
\addlinespace
Intercept & 0.05 & 0.44 & 0.11 & 0.916\\
Emotions: Positive & 0.21 & 0.13 & 1.64 & 0.1\\
Emotions: Negative dominant & -0.18 & 0.11 & -1.65 & 0.099\\
Emotions: Negative submissive & -0.01 & 0.11 & -0.08 & 0.935\\
Attitude to the war & 0.38 & 0.12 & 3.25 & 0.001\\
\addlinespace
Group-based moral shame & -0.36 & 0.17 & -2.1 & 0.036\\
Group-based image shame & 0 & 0.15 & <0.01 & 0.999\\
Group-based guilt & -0.11 & 0.09 & -1.2 & 0.231\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:Table1}Predicting group-based guilt and shame from political beliefs}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Moral Shame} & \multicolumn{4}{c}{Image Shame} & \multicolumn{4}{c}{Guilt} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
  & $\beta$ & $b$ & $SE$ & $p$ & $\beta$ & $b$ & $SE$ & $p$ & $\beta$ & $b$ & $SE$ & $p$\\
\midrule
Intercept & 0 & -2.89 & 0.32 & <.001 & 0 & -2.85 & 0.34 & <.001 & 0 & -2.93 & 0.34 & <.001\\
Democratic Values & 0.41 & 0.64 & 0.05 & <.001 & 0.4 & 0.64 & 0.05 & <.001 & 0.41 & 0.65 & 0.05 & <.001\\
Political Cynicism (politicians) & 0.18 & 0.2 & 0.05 & <.001 & 0.16 & 0.18 & 0.05 & <.001 & 0.09 & 0.1 & 0.05 & .039\\
Political Cynicism (politics) & -0.05 & -0.05 & 0.04 & .189 & -0.03 & -0.03 & 0.04 & .458 & -0.03 & -0.03 & 0.04 & .455\\
Political Alienation & -0.05 & -0.06 & 0.04 & .122 & -0.03 & -0.04 & 0.04 & .380 & 0.01 & 0.02 & 0.04 & .663\\
\addlinespace
Political Responsibility & 0.04 & 0.05 & 0.04 & .190 & 0.03 & 0.04 & 0.04 & .347 & 0.07 & 0.1 & 0.04 & .022\\
\midrule
R$^{2}$ &  & .260 &  &  &  & .234 &  &  &  & .221 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:Table2}Predicting anti-war action from group-based guilt and shame}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Past Behaviour} & \multicolumn{4}{c}{Behavioural Intention} & \multicolumn{4}{c}{Action Probability} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
  & $\beta$ & b & SE & p & $\beta$ & b & SE & p & $\beta$ & b & SE & p\\
\midrule
Intercept & 0 & 0.1 & 0.04 & .009 & 0 & 1.09 & 0.03 & <.001 & 0 & 1.21 & 0.07 & <.001\\
Guilt & 0.02 & 0.01 & 0.04 & .756 & 0 & 0 & 0.03 & .942 & 0.05 & 0.06 & 0.06 & .326\\
Image Shame & -0.07 & -0.05 & 0.05 & .393 & 0.1 & 0.06 & 0.04 & .154 & -0.02 & -0.02 & 0.1 & .826\\
Moral Shame & 0.48 & 0.31 & 0.06 & <.001 & 0.56 & 0.33 & 0.05 & <.001 & 0.59 & 0.77 & 0.11 & <.001\\
\midrule
R$^{2}$ &  & .181 &  &  &  & .425 &  &  &  & .376 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

Behavioral intentions and action probability correlated at \emph{r} = 0.86, \emph{p} \textless.001, so we scaled and combined the two measures into a single indicator of future anti-war action. We ran a linear regression predicting future anti-war behavior from attitude towards the war, negative and positive emotions, and shame and guilt. Table \ref{tab:Table3} presents the results. Overall, the model explained 47\% of variance in future behavior. Anti-war behavioral intentions were best predicted by moral shame (\(\beta\) = 0.36, \emph{p} \textless.001), followed by negative dominant emotions (\(\beta\) = 0.24, \emph{p} \textless.001), and only then attitude (\(\beta\) = -0.15, \emph{p} \textless.001). Negative submissive emotions had a small negative effect on intentions to act (\(\beta\) = -0.08, \emph{p} = .015).

@@

\caption{\label{tab:Table3}Predicting future behavior from emotions and attitudes
}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
  & $\beta$ & b & SE & t-value & p\\
\midrule
Intercept & 0 & -0.1 & 0.12 & -0.82 & .410\\
Emotions: Positive & -0.032 & -0.03 & 0.03 & -0.96 & .337\\
Emotions: Negative Dominant & 0.237 & 0.19 & 0.03 & 6.4 & <.001\\
Emotions: Negative Submissive & -0.076 & -0.07 & 0.03 & -2.43 & .015\\
Attitudes towards the war & -0.152 & -0.12 & 0.03 & -3.77 & <.001\\
\addlinespace
Group-based moral shame & 0.36 & 0.22 & 0.05 & 4.63 & <.001\\
Group-based image shame & 0.002 & 0 & 0.04 & 0.03 & .977\\
Group-based guilt & 0.033 & 0.02 & 0.03 & 0.76 & .450\\
\bottomrule
\end{tabular}
\end{table}

The results of the zero-inflated negative binomial model (Table \ref{tab:TableS4}, SM) suggested that different predictors account for the presence vs.~absence of intentions to act versus the strength of these intentions. Only moral shame (\emph{b} = -0.36, \emph{p} = .036) and attitude (\emph{b} = 0.38, \emph{p} = .001) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (\emph{b} = 0.24, \emph{p} = \textless.001), whereas negative submissive emotions predicted weaker intentions to act (\emph{b} = -0.14, \emph{p} = .013).

@@

\caption{\label{tab:TableS1}Path model predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
\em{ } & \em{b} & \em{SE} & \em{Z} & \em{p} & \em{$\beta$}\\
\midrule
\em{\textbf{Guilt}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
Democratic values & 0.65 & 0.05 & 12.28 & <.001 & 0.41\\
Political cynicism (politicians) & 0.1 & 0.05 & 2.15 & .032 & 0.09\\
Political cynicism (politics) & -0.03 & 0.05 & -0.69 & .492 & -0.03\\
Political alienation & 0.02 & 0.04 & 0.44 & .663 & 0.01\\
\addlinespace
Political responsibility & 0.1 & 0.05 & 2.19 & .028 & 0.07\\
\em{\textbf{Image shame}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
Democratic values & 0.64 & 0.05 & 12.13 & <.001 & 0.4\\
Political cynicism (politicians) & 0.18 & 0.05 & 3.85 & <.001 & 0.16\\
Political cynicism (politics) & -0.03 & 0.05 & -0.69 & .489 & -0.03\\
\addlinespace
Political alienation & -0.04 & 0.04 & -0.92 & .359 & -0.03\\
Political responsibility & 0.04 & 0.04 & 0.94 & .345 & 0.03\\
\em{\textbf{Moral shame}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
Democratic values & 0.64 & 0.05 & 12.61 & <.001 & 0.41\\
Political cynicism (politicians) & 0.2 & 0.04 & 4.52 & <.001 & 0.18\\
\addlinespace
Political cynicism (politics) & -0.05 & 0.04 & -1.21 & .228 & -0.05\\
Political alienation & -0.06 & 0.04 & -1.53 & .125 & -0.05\\
Political responsibility & 0.05 & 0.04 & 1.3 & .195 & 0.04\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS2}Zero-inflated negative binomial regression predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrr}
\toprule
\multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Moral Shame}} & \multicolumn{3}{c}{\textbf{Image Shame}} & \multicolumn{3}{c}{\textbf{Guilt}} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
\em{ } & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & -0.76 & 0.31 & .014 & -0.44 & 0.29 & .129 & -0.85 & 0.28 & .002\\
Democratic values & 0.23 & 0.05 & <.001 & 0.17 & 0.05 & <.001 & 0.25 & 0.05 & <.001\\
Political cynicism (politicians) & 0.12 & 0.05 & .006 & 0.12 & 0.04 & .005 & 0.07 & 0.04 & .065\\
Political cynicism (politics) & -0.04 & 0.03 & .172 & -0.03 & 0.03 & .253 & -0.02 & 0.03 & .548\\
\addlinespace
Political alienation & -0.03 & 0.03 & .255 & 0 & 0.03 & .971 & 0 & 0.03 & .992\\
Political responsibility & 0.01 & 0.03 & .691 & 0 & 0.03 & .948 & 0.03 & 0.03 & .308\\
\midrule
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 5.03 & 0.63 & <.001 & 5.15 & 0.62 & <.001 & 4.17 & 0.6 & <.001\\
Democratic values & -0.74 & 0.1 & <.001 & -0.77 & 0.1 & <.001 & -0.67 & 0.09 & <.001\\
\addlinespace
Political cynicism (politicians) & -0.05 & 0.09 & .529 & -0.06 & 0.08 & .493 & 0.05 & 0.08 & .569\\
Political cynicism (politics) & -0.11 & 0.07 & .115 & -0.11 & 0.07 & .123 & -0.07 & 0.07 & .315\\
Political alienation & 0.02 & 0.07 & .730 & 0.04 & 0.07 & .579 & -0.06 & 0.07 & .369\\
Political responsibility & -0.05 & 0.07 & .528 & -0.05 & 0.07 & .492 & -0.07 & 0.07 & .295\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS3}Predicting anti-war action from group-based shame and guilt}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrr}
\toprule
\multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Past behavior}} & \multicolumn{3}{c}{\textbf{Behavioral inention}} & \multicolumn{3}{c}{\textbf{Action probability}} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
\em{ } & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 0.65 & 0.16 & <.001 & -0.22 & 0.15 & .142 & 0.39 & 0.1 & <.001\\
Guilt & 0 & 0.07 & .953 & -0.03 & 0.05 & .530 & 0.02 & 0.04 & .606\\
Image shame & -0.09 & 0.09 & .313 & 0 & 0.08 & .988 & 0.02 & 0.06 & .671\\
Moral shame & 0.08 & 0.1 & .451 & 0.25 & 0.08 & .003 & 0.22 & 0.07 & <.001\\
\midrule
\addlinespace
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 2.72 & 0.19 & <.001 & 1.7 & 0.2 & <.001 & 1.4 & 0.14 & <.001\\
Guilt & -0.05 & 0.13 & .696 & -0.18 & 0.13 & .156 & -0.2 & 0.09 & .033\\
Image shame & -0.18 & 0.17 & .295 & -0.47 & 0.26 & .076 & -0.13 & 0.14 & .384\\
Moral shame & -0.65 & 0.19 & <.001 & -0.26 & 0.27 & .337 & -0.35 & 0.16 & .033\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS4}Predicting future behavior from emotions and attitudes.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrr}
\toprule
\em{ } & \em{b} & \em{SE} & \em{z-value} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 1.63 & 0.23 & 7.05 & <.001\\
Emotions: Positive & -0.08 & 0.08 & -1.06 & .287\\
Emotions: Negative dominant & 0.24 & 0.06 & 4.32 & <.001\\
Emotions: Negative submissive & -0.14 & 0.05 & -2.49 & .013\\
\addlinespace
Attitude to the war & -0.12 & 0.07 & -1.84 & .066\\
Group-based moral shame & 0 & 0.06 & -0.05 & .964\\
Group-based image shame & 0.08 & 0.05 & 1.5 & .133\\
Group-based guilt & 0.05 & 0.04 & 1.51 & .132\\
\midrule
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
\addlinespace
Intercept & 0.05 & 0.44 & 0.11 & .916\\
Emotions: Positive & 0.21 & 0.13 & 1.64 & .100\\
Emotions: Negative dominant & -0.18 & 0.11 & -1.65 & .099\\
Emotions: Negative submissive & -0.01 & 0.11 & -0.08 & .935\\
Attitude to the war & 0.38 & 0.12 & 3.25 & .001\\
\addlinespace
Group-based moral shame & -0.36 & 0.17 & -2.1 & .036\\
Group-based image shame & 0 & 0.15 & <0.01 & .999\\
Group-based guilt & -0.11 & 0.09 & -1.2 & .231\\
\bottomrule
\end{tabular}
\end{table}
